Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2020-02-27 xrb/paper.tex
Added sentence discussing running the 10/10 iso7 simulation to 15 ms instead of 20 ms with aprox13.
Add space after the typeset code name "Castro" in section 6.

We also considered the effect of the network size.
Figure~\ref{fig:network} shows a comparison of the 10/10 boosting run
with the standard 13-isotope {\tt aprox13} network and the reduced
7-isotope {\tt iso7} network.  We see that the flame in the {\tt aprox13}
case is slightly more advanced and has a higher $\bar{A}$ than the {\tt iso7}
case.  We see in the next section that these two networks give largely
the same flame speed.  The reduced network size saves a lot of memory,
which will be useful when we transition to 3D simulations.

@@

In addition to exploring other aspects of the XRB physics, there are several changes to the algorithm used to
model these XRBs we will pursue.  First, as shown in \citet{castro-sdc}, we have
developed a fourth-order (in space and time) method for coupling
hydrodynamics and reactions that should greatly improve the accuracy
of the simulations.  We expect that by using this new high-order
algorithm we can drop a level of refinement from the simulations while
still accurately modeling the evolution.  We have also ported
\castro\ to GPUs, giving an order of magnitude performance boost on
nodes with both CPUs and GPUs.  Flames without any boosting are currently running
using the new GPU-enabled \castro and will be the focus of the next study.

>>>>

We also considered the effect of the network size.
Figure~\ref{fig:network} shows a comparison of the 10/10 boosting run
with the standard 13-isotope {\tt aprox13} network and the reduced
7-isotope {\tt iso7} network.  We see that the flame in the {\tt aprox13}
case is slightly more advanced and has a higher $\bar{A}$ than the {\tt iso7}
case.  We see in the next section that these two networks give largely
the same flame speed.
We only ran the 10/10 simulation with the {\tt iso7} reaction network to 15~ms,
and we observe this was sufficient to establish its steady flame speed for comparison to our 10/10 simulation with the {\tt aprox13} network.
The reduced network size saves a lot of memory,
which will be useful when we transition to 3D simulations.

@@

In addition to exploring other aspects of the XRB physics, there are several changes to the algorithm used to
model these XRBs we will pursue.  First, as shown in \citet{castro-sdc}, we have
developed a fourth-order (in space and time) method for coupling
hydrodynamics and reactions that should greatly improve the accuracy
of the simulations.  We expect that by using this new high-order
algorithm we can drop a level of refinement from the simulations while
still accurately modeling the evolution.  We have also ported
\castro\ to GPUs, giving an order of magnitude performance boost on
nodes with both CPUs and GPUs.  Flames without any boosting are currently running
using the new GPU-enabled \castro\ and will be the focus of the next study.
